### 2024-06-05 Scripts/Manuscript_scripts.Rmd
Update Manuscript_scripts.Rmd

>>>>

```{r Fig 2j}

```{r Fig S2a}

df_species_selected <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\MDS_metrics-bray+species_abundance-species_pneumonia.csv)')
df_species_selected$SamplingSite  <- str_replace_all(df_species_selected$SamplingSite, "-", "")
df_species_selected$variable <- str_split(df_species_selected$variable, "__", simplify = TRUE)[,2]
df_species_selected$variable  <- str_replace_all(df_species_selected$variable, "_", " ")
df_species_selected$variable  <- str_replace_all(df_species_selected$variable, " group", " ")

my_comparisons <- list( c("HospitalA", "HospitalB"), c("HospitalA", "HospitalC"), c("HospitalB", "HospitalC") )
df_species_selected$SamplingSite <- factor(df_species_selected$SamplingSite,levels = c("HospitalA", "HospitalB","HospitalC"))

p_species_selected <- ggboxplot(df_species_selected, "SamplingSite", "value",
                             color = "SamplingSite", palette =c("#e64833", "#01a188", "#3e5386"),
                             add = "jitter",add.params = list(size = 2, alpha = 0.5))  +
  stat_boxplot(mapping = aes(color=SamplingSite),geom = "errorbar",width=0.05)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",
                     size=5.0,vjust=.1,tip.length= c(0,0,0)) + ylim(-1,135) +
  facet_grid(~variable) + labs(x=NULL,y='Relative abundance (%)') +
  theme_pubr(base_size = 15,border = T,legend ='none',x.text.angle = 30) +
  theme(strip.text.x = element_text(size = 14))      
p_species_selected

```{r Fig S2b}

df_top_pathabundance <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\humann3-top_pathabundance-each_hospital-merged_top.csv)')
df_metadata <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\humann3_metadata.csv)')
matrix_top_abundance <- as.matrix(df_top_pathabundance[,-1])
row.names(matrix_top_abundance) <- df_top_pathabundance$pathway
matrix_top_abundance_log <- log10(matrix_top_abundance)
matrix_top_abundance_log[is.infinite(matrix_top_abundance_log)] <- 0
plot_top_pathabundance <- Heatmap(matrix_top_abundance_log,show_column_names = T,show_row_names = T,cluster_columns = F,cluster_rows = T,
        rect_gp = gpar(col= "grey"),name='Abundance (log10)',
        row_names_gp = gpar(fontsize=20),column_names_gp = gpar(fontsize=20),
        heatmap_legend_param = list(title_gp = gpar(fontsize=20),labels_gp = gpar(fontsize=20)))

```{r Fig S2c}

df_tempral_dyanmics_group_new_criteria <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\OI+WBC+Neutrophils-temporal_dynamics_groups.csv)')
df_tempral_dyanmics_group_new_criteria$Group <- factor(df_tempral_dyanmics_group_new_criteria$Group,levels =c('multiple','stable') )
df_tempral_dyanmics_groups_no_na <- na.omit(df_tempral_dyanmics_groups)
my_comparisons <- list(c('multiple','stable'))
df_tempral_dyanmics_group_new_criteria_OI <- df_tempral_dyanmics_group_new_criteria[!is.na(df_tempral_dyanmics_group_new_criteria$Oxygenation.Index.of.The.Day), ]

ggboxplot(df_tempral_dyanmics_group_new_criteria_OI, x="Group", y="Oxygenation.Index.of.The.Day",
          color = "Group",palette =c("#E8080A", "#0A74B2"),
          add = "jitter",add.params = list(size =2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Group), lwd = 0.7) +
  scale_x_discrete(labels = c("multiple" = "Multi-dominant", "stable" = "Mono-dominant")) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
  labs(x=NULL,y='Oxygenation index',)  +
  theme_pubr(base_size = 21,legend ='none',x.text.angle = 30)

df_tempral_dyanmics_group_new_criteria_neutrophil <- df_tempral_dyanmics_group_new_criteria[!is.na(df_tempral_dyanmics_group_new_criteria$The.Percentage.of.Neutrophils.on.The.Day.of.Sampling), ]
ggboxplot(df_tempral_dyanmics_group_new_criteria_neutrophil, x="Group", y="The.Percentage.of.Neutrophils.on.The.Day.of.Sampling",
          color = "Group",palette =c("#E8080A", "#0A74B2"), 
          add = "jitter",add.params = list(size =2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Group), lwd = 0.7) +
  scale_x_discrete(labels = c("multiple" = "Multi-dominant", "stable" = "Mono-dominant")) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
  labs(x=NULL,y='Percentage of neutrophils (%)',) +  
  theme_pubr(base_size = 21,legend ='none',x.text.angle = 30)

```{r Fig 3a}

df_arg_num = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\RGI_profile-comparisons_arg_number.csv)")
df_arg_num$species <- factor(df_arg_num$species,levels = c('pseudomonas','acinetobacter','klebsiella','corynebacterium','stenotrophomonas'))
my_comparisons <- list(c('pseudomonas','stenotrophomonas'),c('pseudomonas','corynebacterium'),
                       c('acinetobacter','stenotrophomonas'),c('acinetobacter','corynebacterium'),
                       c('klebsiella','stenotrophomonas'),c('klebsiella','corynebacterium'))

map <-c('acinetobacter'=3.965,'pseudomonas'=6.644,'klebsiella'=5.596,'corynebacterium'=2.841,'stenotrophomonas'=4.613)
df_arg_num <- df_arg_num %>%
  mutate(genome_length = map[species])
df_arg_num <- df_arg_num %>%
  mutate(arg_num_normalized = arg_num/genome_length)

ggboxplot(df_arg_num, x="species", y="arg_num_normalized",
          color = "species", palette =c("#E41A1C","#377EB8","#4DAF4A","#984EA3","#FF7F00","#F781BF","#A65628","#F781BF"),
          add = "jitter",add.params = list(size = 2, alpha = 0.5))  +
  stat_boxplot(mapping = aes(color=species),geom = "errorbar",width=0.1,lwd=0.8) +
  stat_compare_means(comparisons = rev(my_comparisons),label = "p.label",size=10,
                     vjust=.15,tip.length= c(0,0,0)) +
  scale_x_discrete(labels=c('P. aeruginosa','A. baumannii','K. pneumoniae','C. striatum','S. maltophilia'))+
  labs(x=NULL,y='Number of ARGs (Normalized)',) +  
  theme_pubr(base_size = 32,legend ='none',x.text.angle = 30)

```{r Fig 3b}
df_meta_argname <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\RGI_profile-species_all-metadata-arg_acronym.csv)')

dend_species_all <- ReadDendrogram(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\inputfiles.tre-test.nwk)")
tree_species_all <- read.tree(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\inputfiles.tre.nwk)")
order_row <- data.frame(species=tree_species_all$tip.label)

plot_heatmap_species_all <- Heatmap(t(matrix_rgi_species_all),
                                    #breaks = c(0,1,3),
                                    col = c('#ffffff','#ff0000'),
                                    # col = c('#f7faff','#08306b'),
                                    left_annotation  = rowAnnotation(df=labels_annotation_col,
                                                                     col=list(species=c(corynebacterium="#e36255", stenotrophomonas="#ec9a86",
                                                                                        pseudomonas="#a2c5c9", klebsiella="#f3c262", 
                                                                                        acinetobacter="#f1e0ce"))),
                                    #                                     col = list(category=c(core='#16519f',accessory='#f07e74'))),
                                    # row_split = factor(labels_annotation_col[,1],levels = c("corynebacterium",'stenotrophomonas','klebsiella','pseudomonas',"acinetobacter")),
                                    # row_split = c(30,9,12,13,27),
                                    #border_color = NA,
                                    # cluster_rows =as.dendrogram(dendrogram),
                                    # cluster_rows = F,
                                    cluster_columns =T,
                                    # cluster_rows = F,cluster_columns =T,
                                    show_column_dend = F,show_row_dend = T,rect_gp = gpar(col= "grey"),
                                    show_column_names = T,show_row_names = T,
                                    row_order = order_row$species)
